Differences in Homicide Case Information Indicates Why Justice is Not Served

### 2024-12-02 paper/paper.qmd
Updated title of paper

---
title: "Differences in Homicide Case Characteristics Indicates Why Justice is Not Served"
subtitle: "An analysis of solved and unsolved homicides from 2010 to 2017 in one of the United States's 2 largest cities, Chicago and Los Angeles"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-model-result-ci
#| fig-cap: The credible intervals (line) for coefficient estimates (dot) of predictor variables for homicides that go unsolved from 2010 to 2017.
#| echo: false
#| warning: false
#| message: false
# Specify credible interval to be 90% and present model results
modelplot(unsolved_model_results, conf_level = 0.9) +
  labs(x = "90 per cent credible interval")
```

>>>>

---
title: "Differences in Homicide Case Information Indicates Why Justice is Not Served"
subtitle: "An analysis of solved and unsolved homicides from 2010 to 2017 in one of the United States's 2 largest cities, Chicago and Los Angeles"
author: 
  - Emily Su
thanks: "Code and data are available at: [https://github.com/moonsdust/unsolved-murders](https://github.com/moonsdust/unsolved-murders)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    toc: true
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-model-result-ci
#| fig-cap: The credible intervals (line) for coefficient estimates (dot) of predictor variables for homicides that go unsolved from 2010 to 2017.
#| echo: false
#| warning: false
#| message: false
# Specify credible interval to be 90% and present model results
modelplot(unsolved_model_results, conf_level = 0.9) +
  labs(x = "90 per cent credible interval")
```
@tbl-model-result and @fig-model-result-ci
